True versus apparent shapes of bow shocks and bow waves

### 2017-11-15 papers/Paper1/app-dust-wave.tex
Finish 1-d on-axis dust drag description

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-coupling-1d}
  \caption{Dust-gas coupling for an on-axis (purely radial) trajectory
    with \(\alpha\drag = 0.5\). (a)~Grain velocity (in units of
    \(v_\infty\)) and radius (in units of \(R_0\)) versus time. (b)~Phase
    space trajectory. Grain spirals in on point
    \((x, u) = (\alpha\drag^{-1}, 0)\).}
  \label{fig:dust-coupling-1d}
\end{figure}

@@

Considering the incoming flow on the symmetry axis, at each radius
there is an asymptotic gas--grain drift speed, \(w\drift\), for which
the radiative and drag forces exactly cancel, \(f\drag = -\frad\),
yielding
\begin{equation}
  \label{eq:dust-wdrift}
  w\drift = \left( \frac{\Qp L} {4\pi c Q\drag \rho\gas R^2} \right)^{1/2} \ .
\end{equation}
Any deviation of \(w\) from \(w\drift\) produces unbalanced forces
that tend to restore \(w \to w\drift\).  We define a dimensionless
coupling coefficient, \(\alpha\drag\), to be the speed of the incoming
stream in units of the drift velocity at the radiative stagnation
radius:
\begin{equation}
  \label{eq:dust-alpha}
  \alpha\drag \equiv \frac{v_\infty} {w\drift(R_0)} = \left(
    Q\drag \frac{R_0 / a\grain} {\rho\grain / \rho\gas}
  \right)^{1/2} \ ,
\end{equation}
where we have used equation~\eqref{eq:dust-r0} and suppressed a
grain-shape dependent geometric factor of order unity.  If
\(\alpha\drag \ll 1\), then \(w\drift \gg v_\infty\) out to several times the
stagnation radius, so the radiation field has no difficulty in
effectively decoupling the grain from the gas and producing the
velocity difference, \(w = 2 v_\infty\), that is required to turn the grain
around and expel it towards the direction whence it came.  However,
for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of \(w\drift\)
(eq.~\eqref{eq:dust-wdrift}) means that the grain will
\textit{re-couple} to the inflowing gas stream around a radius
\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  This
behavior is illustrated in Figure~\ref{fig:dust-coupling-1d}, where it can be seen that

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/dust-coupling-1d}
  \caption{Dust-gas coupling for an on-axis (purely radial)
    trajectory.  (a)~Grain radial position, \(R/R_0\), gas--grain
    velocity difference, \(w/v_\infty\), and local asymptotic drift
    velocity, \(w\drift/v_\infty\), versus time for
    \(\alpha\drag = 0.5\).  (b)~Phase space (position, velocity)
    trajectories for \(\alpha\drag = 0\), 0.5, and 2. For
    \(\alpha\drag > 0\), the grain spirals in on the point
    \((x, u) = (\alpha\drag^{-1}, 0)\).}
  \label{fig:dust-coupling-1d}
\end{figure}

@@

Considering the incoming flow on the symmetry axis, at each radius
there is an asymptotic gas--grain drift speed, \(w\drift\), for which
the radiative and drag forces exactly cancel, \(f\drag = -\frad\),
yielding
\begin{equation}
  \label{eq:dust-wdrift}
  w\drift = \left( \frac{\Qp L} {4\pi c Q\drag \rho\gas R^2} \right)^{1/2} \ .
\end{equation}
Any deviation of \(w\) from \(w\drift\) produces unbalanced forces
that tend to restore \(w \to w\drift\).  We define a dimensionless
coupling coefficient, \(\alpha\drag\), to be the speed of the incoming
stream in units of the drift velocity at the radiative stagnation
radius:
\begin{equation}
  \label{eq:dust-alpha}
  \alpha\drag \equiv \frac{v_\infty} {w\drift(R_0)} = \left(
    Q\drag \frac{R_0 / a\grain} {\rho\grain / \rho\gas}
  \right)^{1/2} \ ,
\end{equation}
where we have used equation~\eqref{eq:dust-r0} and suppressed a
grain-shape dependent geometric factor of order unity.  If
\(\alpha\drag \ll 1\), then \(w\drift \gg v_\infty\) out to several times the
stagnation radius, so the radiation field has no difficulty in
effectively decoupling the grain from the gas and producing the
velocity difference, \(w = 2 v_\infty\), that is required to turn the grain
around and expel it towards the direction whence it came.  However,
for non-zero \(\alpha\drag\) the \(R^{-1}\) dependence of \(w\drift\)
(eq.~\eqref{eq:dust-wdrift}) means that the grain will
\textit{re-couple} to the inflowing gas stream around a radius
\(\approx R_0 / \alpha\drag \) and be swept in again for another try.  A further
effect of increasing \(\alpha\drag\) is that the grain penetrates closer to
the star on its initial approach, thanks to the tail wind provided by
the gas flow.  Both these behaviors are illustrated in
Figure~\ref{fig:dust-coupling-1d}, where it can be seen that the grain
inertia means that \(w\) lags behind the changes in \(w\drift\) and
the phase space trajectory is spiral, converging on the point
\((R, v) = (R_0 / \alpha\drag, 0)\).
